---
title: "R trends in 2015"
author: "Max Gordon"
date: "8 February 2016"
output: 
  ioslides_presentation:
    logo: ki_logo_square.png
    widescreen: no
---

## What happened?

- Packages
- Adaptation
- Miscellaneous


## Biggest package trends

<div class="columns-2">
**2015**

1. xml2 (Hadley)
2. rversions
3. git2r (Stefan W.)
4. ...
5. DiagrammeR
6. DT


**2012-2013**

1. knitr
2. dplyr
3. shiny
4. stringi/stringr
5. R6
</div>

### Major themes

- web
- graphics
- package building blocks

## xml2{.smaller}

Author: Hadley

<div class="columns-2">
```{r}
library("xml2")
txt <- 
"<foo> 
  <bar> text <baz/> 
  </bar>
</foo>"
x <- read_xml(txt)
x

xml_children(x)

xml_find_all(x, "//baz")
```
</div>

## rversions{.smaller}

```{r}
library(rversions)
rversions::r_release()

rversions::r_versions() %>% 
  head
```

## The R-consortium

Chair: **Hadley W.**

From the about page:

* Create infrastructure and standards to benefit all
* Promote the R language in industry, academia, and government.
* Create and promote best practices.

Members: Microsoft, RStudio, TIBC, Google, HP, Oracle, ...

## R-Hub

*R-Hub will modernize and improve the entire process of developing and testing R packages*

### Goals

1. Services that ease all steps the R package development process, creating a package, building binaries and continuous integration, publishing, distributing and maintaining it.
2. Make these services free for all members of the community.
3. Allow community contributions to r-hub itself.
4. Make CRAN maintainers' work easier by pre-testing CRAN package submissions.

